plackett_luce_monster

### 2022-07-04 inst/plackett_luce_monster.Rmd
further thoughts on nonindependence

The statistical model is as follows.  If a runner finishes, then he
cheers on all his friends who are still running, thereby adding to
their strength.  This is a very simple form of non-independence.

>>>>

There seem to be a few distinct statistical models for nonindependence:

* Runner $i$ might wish to support $j$.  If runner $i$ finishes, once
  his rank is established he might be able to help $j$ in some way.
  He might cheer his still-running friend.  In general, we can
  consider $n$ ordered pairs $(i_r,j_r)$, $1\leq r\leq n$, with runner
  $i_1$ helping runner $j_1$, runner $i_2$ helping $j_2$, and so on.
  One simple case would be equivalence classes of
  $[n]=\{1,2,\ldots,n\}$ with each equivalence class comprising
  mutually supporting runners.  In this model, with a pair of mutually
  supporting runners only the higher-placed competitor can affect the
  other.  The causation is not symmetrical.
* Runner $i$ might hate runner $j$.  If $i$ finishes, he might expend
  his spare energy hinderig $j$ (by throwing stones, for example).
  Note that equivalence classes of mutual hatred might exist.  Again
  note that the link is not symmetrical.
* The help or hindrance discussed above might be contingent on
  placing: perhaps only the winnner (that is, first-placing
  competitor) would be able to influence other competitors.  Or maybe
  competitors with any placing could influence other competitors.
* Runners $i$ and $j$ might elect to cross the finishing line holding
  hands, with the apparent tie broken randomly.  This would be a
  symmetrical relationship.  In general, we could consider
  hand-holding equivalence classes.
* We might have a resource allocation problem, with runners having a
  certain [possibly unknown] amount of "strength" but also the ability
  to expend this strength on objectives other than ranking in the
  race.  A runner might be able to expend just enough energy to remain
  slightly ahead of a rival, reserving energy for other purposes.  If
  runner $i$ wishes to beat runner $j$, and has sufficient resources
  to do so, then runners $i$ and $j$ will finish consecutively with
  $i$ ahead of $j$.
